Bayesian Inference Using Sequential Monte-Carlo Algorithm for Dynamic System Models

### 2020-08-08 MSc-dissertation.tex
New para

\begin{enumerate}
    \item 
\end{enumerate}

@@

\begin{figure}[t!]
    \begin{center}
        \resizebox{1.0\hsize}{!}{\includegraphics{fig/smc.png}}
    \end{center}

>>>>

\begin{enumerate}
    \item Set a threshold schedule $\{\epsilon_1, \epsilon_2, ..., \epsilon_T\}$ where $T$ is the total number of populations and $\{\epsilon_1, \epsilon_2, ..., \epsilon_T\}$ is a descending sequence; set the number of particles in each population as $N$, set the population index $t=1$
    \item if $t=1$, draw samples from prior distribution until $N$ particles are accepted under threshold $\epsilon_1$, i.e. each of $N$ particles s.t. $d(D,D^*)<\epsilon_1$

    Else ($t>1$), draw samples from previous population $\{\theta^*_{t-1}\}$ with weights $\{w_{t-1}\}$, perturb the particles using a perturbation kernel $K(\theta^*|\theta)$ and obtain $\theta^{**}\sim K(\theta^*|\theta)$
    \item Repeat step 2 until $N$ particles are accept under threshold $\epsilon_t$
    \item Calculate the weights of the accepted particles. For particle $i$ 
    \begin{align}
        \label{eq:weight}
        w^i_t =\begin{cases}
            1 & \text{if t=1} \\
            \frac{p(\theta^i_t)}{\sum_{j=1}^{N} w^j_{t-1}K(\theta^j_t|\theta^j_{t-1})} & \text{if t $\neq$ 1} 
        \end{cases}
    \end{align}

    \item Normalise $\{w^i_t\}$, increase population index $t$ by 1
    \item Repeat step 2, 3 and 4 until $t>N$
    \item Output the accepted particles $\{\theta^*_{t}\}$ and their weights $\{w^i_t\}$ in each generation $t$

\end{enumerate}

An illustrative graph of the ABC SMC procedures can be found in Figure \ref{fig:smc}.

\begin{figure}[t]
    \begin{center}
        \resizebox{1.0\hsize}{!}{\includegraphics{fig/smc.png}}
    \end{center}

@@

% \begin{figure}[t!]
%     \begin{center}
%         \resizebox{1.0\hsize}{!}{\includegraphics{fig/smc.png}}
%     \end{center}

%     \caption[ABC SMC sampling process]%
%     {ABC SMC sampling process. $\theta^*$ denotes a sample drawn from previous population, which is used to generate simulated data $D^*$. $d$ is a distance measurement, $d(D^*,D)$ represents the discrepancy between observed data and simulated data. for each population $t$, $\epsilon_t$ is a threshold criterion to determine whether to accept that drawn sample}
%     \label{fig:smc}
